Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens

### 2014-01-29 limits/ms.tex
Justin further changes - see E-mail

%For deprojection algorithm: 
\newcommand{\cth}[1][]{\cos^{#1}\theta}
\newcommand{\sth}[1][]{\sin^{#1}\theta}
\def\dth{{\rm d}\theta}

@@

\begin{abstract}
We use a new non-parametric gravitational modelling tool -- \Glass\ -- to
determine what quality of data (strong lensing, stellar kinematics, and/or
stellar masses) are required to measure the circularly averaged mass profile of
a lens and its shape. \Glass\ uses an under-constrained adaptive grid of mass
pixels to model the lens, searching through thousands of models to marginalise
over model uncertainties. Our key findings are as follows: (i) for pure lens
data, multiple sources with wide redshift separation give the strongest
constraints as this breaks the well-known mass-sheet or steepness degeneracy;
(ii) a single quad with time delays also performs well, giving a good recovery
of both the mass profile and its shape; (iii) stellar masses -- for lenses
where the stars dominate the central potential -- can also break the steepness
degeneracy, giving a recovery almost as good as having time delay data or
multiple source redshifts; (iv) stellar kinematics provide a robust measure of
the mass at the half light radius of the stars $r_{1/2}$ that can also break
the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v)
if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the
stellar velocity anisotropy $\beta$ -- an interesting quantity in its own
right. Where information on the mass distribution from lensing and/or other
probes becomes redundant, this opens up the possibility of using strong lensing
to constrain cosmological models. 
\end{abstract}

@@

To see why lens modelling details are of crucial importance, let us
recall the essential quantities that appear in lensing.\footnote{These
  quantities are defined more precisely in \S\ref{sec:lensing_basic}.}
First we have the distances. Let $D_L$, $D_S$, $D_{LS}$ be the
angular-diameter distances to the lens, source, and from lens to
source; these are all proportional to $c/H_0$ but have factors
that depend on the particular choice of cosmology.  Typically:
%
\begin{equation}
D_L \approx z \frac c{H_0}\ \hbox{and}\ \frac{D_S}{D_{LS}} \sim 1.
\end{equation}
%
For multiple images, the sky-projected density must exceed the critical
density
%
\begin{equation}
\Sigma_\mathrm{crit} = \frac{D_S}{D_{LS}} \Sigma_L = \frac{D_S}{D_{LS}} \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
\end{equation}
%
in some region.  The separation between the lensed images is of order
the Einstein radius $\theta_E$, which is related to
the mass by:
%
\begin{equation}
\theta_E \sim \frac{R_G}{D_L} \frac{D_{LS}}{D_S}
\end{equation}
%
where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$) is the gravitational radius. If the source is a
quasar or otherwise rapidly variable, a time delay $\Delta t$ in the variability
will be present where:
%
\begin{equation}
\Delta t \sim R_G/c \,.
\end{equation}
%
So in principle, one can not only measure the mass of the lens, one can use the
dependence on the cosmology-dependent $D$ factors to extract the cosmological
model and all its parameters.  \cite{1937ApJ....86..217Z} drew attention to the
former, and \cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the
latter, all long before lenses were discovered.  The difficulty with actually
doing this, however, became apparent soon after the discovery of the first lens
by \cite{1979Natur.279..381W}.  In the first ever paper on lens modelling,
\cite{1981ApJ...244..736Y} found that many plausible mass distributions could
reproduce the data.

@@

  Being under-constrained, it is then {\it necessary} to explore model
  degeneracies rather than find a single `best-fit'
  solution. Free-form models are more commonly used with cluster
  lenses
  \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S},
  but can be used with galaxy lenses as well, where their less
  restrictive assumptions can be important.  For example, in
  time-delay galaxy lenses, parametric models have historically led to
  tension with independent measures of the Hubble parameter $H_0$
  \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are
  resolved once the less restrictive assumptions of free-form models
  are permitted \citep{2007ApJ...667..645R}.  Hybrid methods, using a
  mass grid on top a parametric model, have also been explored
  \citep[e.g.,][]{2010MNRAS.408.1969V}.

\item Model ensembles, exploring a diverse
  range of possible mass distributions that nonetheless all fit the data,
  are a way of combating the non-uniqueness of models.  Such ensembles are
  possible in parametric models \citep{1999AJ....118...14B} but are more
  common in free-form models
  \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.

\item {\bf Stellar kinematic constraints:} This was first suggested by
  \citet{2002MNRAS.337L...6T} as a means to break lensing
  degeneracies. This works because stellar kinematics can provide an
  independent estimate of the Einstein radius, via the virial theorem:
%
\begin{equation}
  \frac{\langle v^2_\mathrm{los}\rangle}{c^2} \approx
  \frac{\theta_E}{6\pi} \frac{D_S}{D_{LS}}
\label{eqn:virial}
\end{equation}
%
where $\langle v^2_\mathrm{los}\rangle$ is the projected stellar
velocity dispersion, and the above relation becomes exact for
isothermal lenses.  The technique has been applied to many lenses
\citep{2006ApJ...649..599K,2008ApJ...682..964B}.  Going further, the
use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is
especially interesting.

\item {\bf Stellar mass constraints:} The stellar mass in a lens can be
    inferred from photometry and compared with the total mass
    \citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.  Since
    the inferred stellar mass depends on the assumed IMF, lenses in which
    stellar mass dominates can be used to derive upper bounds on the stellar
    $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds on stellar $M/L$ have also
    been claimed \citep{2013MNRAS.428.3183D} but these require upper-bound
    assumptions about the dark-matter profile. \hilight{JR. I feel like we need
    more citations here and throughout. We must be skipping over an Armada of
literature.}

@@

There are three further key modelling ideas in the literature that we will not
touch upon in this present work: to use X-ray intensity and temperature
profiles as a mass constraint \citep[e.g.][]{2013ApJ...765...25N}; and to model
multiple lenses simultaneously, with one or more cosmological parameters
variable but shared between the lenses. This latter strategy has been used to
constrain $H_0$ from time delay lenses
\citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P} and
recently the cosmological parameters $\Omega$ as well
\citep{2014MNRAS.437..600S}.  Third, it is in principle possible to estimate
the $\Omega$ parameters even from a single lens, if there are lensed sources at
multiple redshifts \citep{2014MNRAS.437.2461L} or by using a strong prior
\citep{2010Sci...329..924J,2013arXiv1306.4732S}.

@@

\subsection{A post-processing module for stellar kinematics}\label{sec:glasskinematics} 
Similarly to the null-space constraint (\secref{sec:glassextraimages}), stellar
kinematic constraints constitute a non-linear prior on the mass map and must be
applied in post-processing. We sweep through the model ensemble performing an
Abel deprojection to determine $\Mddd(r)$ from the projected surface density
$\Sigma(R)$ assuming spherical symmetry
\citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}: 
%
\begin{eqnarray} 
    \Mddd(r) & = & M(<r) - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left(\frac{1}{\cth[2]} \right. \nonumber \\ 
    & & \left. - \frac{\sth}{\cth[3]} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
\end{eqnarray}
%
where $M(<r)$ is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.

@@

\begin{enumerate}
\item one double and one extended double;
\item one quad and one extended quad;
\item two 2-source quads with varying redshift contrast.
\end{enumerate}
The `extended' configurations use multiple point sources at the same redshift
to simulate an extended source that will produces an arc-like image.
\figref{arrival surfaces} shows the lens configurations for the \mockBC\
galaxy.  The configurations for the other galaxies are similar. Within the
names, the labels R1, R2, R3, refer to the redshift of the sources. We have
chosen R1=1.72, R2=0.72, and R3=0.51 so that the radial distribution of the
images is nearly equal.

@@

\hilight{[NOT TRUE. Almost any shear is allowed, although in practice, very little is used.]
In all cases, we additionally assume no external shear. This amounts to an
assumption that any such shear field can be constrained by data (e.g. combining
weak lensing constraints, or assuming that the shear field correlates with
visible galaxies -- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).}

@@

We can also more directly probe the recovery of the shape of the mass
distribution by defining a global measure of lens shape
%
\begin{equation} 
    s \equiv \lambda_1/\lambda_2
\end{equation} 
%
where $\lambda_1$ and $\lambda_2$ are the eigenvalues of the 2D inertia tensor
%
% \begin{gather}
%    I_{xx} = \sum_{\vec\theta} M(\vec\theta) \theta^2_y \quad ; \quad
%    I_{yy} = \sum_{\vec\theta} M(\vec\theta) \theta^2_x \\
%    I_{xy} = I_{yx} = - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \nonumber
%    \label{eqn:inertia}
% \end{gather}
%
\begin{equation}
\left(
\begin{matrix}
   \sum_{\vec\theta} M(\vec\theta) \theta^2_y 
    & - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \\
    - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y
    & \sum_{\vec\theta} M(\vec\theta) \theta^2_x
\end{matrix}
\right).
    \label{eqn:inertia}
\end{equation}
%
We always take $\lambda_1$ to be the largest value. As with $f_R$ and
$f_\theta$, we only consider mass up to one radial position passed the
outermost image and compute the fractional error as:
%
\begin{equation} \label{ferror shape}
  f_\mathrm{shape} = \left|s - \tilde s\right|  / \tilde s
\end{equation}
%
where $\tilde s$ is the shape of the mock galaxy. The distribution of
$f_\mathrm{shape}$ for each mock galaxy and each test case is shown in
\figref{shape results}.  Interestingly, for this global shape parameter
recovery it appears more important to have time delay data and/or a central
image (T,M) than to have a quad or multiple sources with wide redshift
separation. In all cases, the stellar mass little-aids the recovery, reflecting
the fact that $s$ is heavily weighted towards the shape at the {\it edge} of
the mass map, rather than at the centre where the stars may dominate the
potential (see \eqnref{eqn:inertia}).

@@

\item Stellar masses -- for lenses
where the stars dominate the central potential -- can also break the steepness
degeneracy, giving a recovery almost as good as having time delay data or
multiple source redshifts;

@@

In this appendix, we explore the effect of the radial symmetry prior.
\figref{fig:no_symm_prior} shows results for a single quad with time delays (top) and an
extended double without time delays (bottom); in both cases, we do not use the stellar mass
constraints. The results for the quad a similarly good to the case with the
radial prior (\figref{reconstruction}); for the double, however, the results
are significantly degraded as expected.

\begin{figure*}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d.pdf}\\
%
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a-1.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b-1.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c-1.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d-1.pdf}\\
%
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-a.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-b.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-c.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-d.pdf}
%
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-a-1.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-b-1.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-c-1.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-d-1.pdf}
\caption{Results for a single quad (upper two rows) and an extended double (lower two rows)
    without the radial symmetry prior; The top row of each group uses time delay data. The stellar
    mass constraint has not been used in any of these examples. Figures and symbols are as in \figref{reconstruction} and
    \figref{2d mass reconstruction}.}
\label{fig:no_symm_prior}
\end{figure*}

>>>>

%For deprojection algorithm: 
\newcommand{\cth}[1][]{\cos^{#1}\theta}
\newcommand{\sth}[1][]{\sin^{#1}\theta}
\def\dth{d\theta}

@@

\begin{abstract}
We use a new non-parametric gravitational modelling tool -- \Glass\ -- to
determine what quality of data (strong lensing, stellar kinematics, and/or
stellar masses) are required to measure the circularly averaged mass profile of
a lens and its shape. \Glass\ uses an under-constrained adaptive grid of mass
pixels to model the lens, searching through thousands of models to marginalise
over model uncertainties. Our key findings are as follows: (i) for pure lens
data, multiple sources with wide redshift separation give the strongest
constraints as this breaks the well-known mass-sheet or steepness degeneracy;
(ii) a single quad with time delays also performs well, giving a good recovery
of both the mass profile and its shape; (iii) stellar masses -- for lenses
where the stars dominate the central potential -- can also break the steepness
degeneracy, giving a recovery for doubles almost as good as having a quad with time delay data, or
multiple source redshifts; (iv) stellar kinematics provide a robust measure of
the mass at the half light radius of the stars $r_{1/2}$ that can also break
the steepness degeneracy if $r_{1/2} \neq r_E$ -- the Einstein radius; and (v)
if $r_E \sim r_{1/2}$, then stellar kinematic data can be used to probe the
stellar velocity anisotropy $\beta$ -- an interesting quantity in its own
right. Where information on the mass distribution from lensing and/or other
probes becomes redundant, this opens up the possibility of using strong lensing
to constrain cosmological models. 
\end{abstract}

@@

To see why lens modelling details are of crucial importance, let us
recall the essential quantities that appear in lensing (see also \S\ref{sec:theory} for a more detailed exposition). First we have the distances. Let $D_L$, $D_S$, $D_{LS}$ be the
angular-diameter distances to the lens, source, and from lens to
source; these are all proportional to $c/H_0$ but have factors
that depend on the particular choice of cosmology\footnote{Here, $c$ is the speed of light in vacuo and $H_0$ is the Hubble parameter.}.  Typically:
%
\begin{equation}
D_L \approx z_L \frac c{H_0}\ \hbox{and}\ \frac{D_S}{D_{LS}} \sim 1.
\end{equation}
where $z_L$ is the redshift of the lens. 
%
For multiple images, the sky-projected density must exceed the critical
density in some region:
%
\begin{equation}
\Sigma_\mathrm{crit} = \frac{D_S}{D_{LS}} \Sigma_L = \frac{D_S}{D_{LS}} \frac{c^2}{4\pi G D_L} \sim \frac{1\rm\,kg\,m^{-2}}{z_L}
\end{equation}
where $G$ is Newton's gravitational constant. 
%
The separation between the lensed images is of order
the Einstein radius $\theta_E$, which is related to
the mass by:
%
\begin{equation}
\theta_E \sim \frac{R_G}{D_L} \frac{D_{LS}}{D_S}
\end{equation}
%
where $R_G = GM/c^2$ (with $M$ the projected mass enclosed within $\theta_E$) is the gravitational radius. If the source is a
quasar or otherwise rapidly variable, a time delay $\Delta t$ in the variability
will be present where:
%
\begin{equation}
\Delta t \sim R_G/c \,.
\end{equation}
%
So in principle, one can not only measure the mass of the lens, one can use the
dependence on the cosmology-dependent $D$ factors to extract the cosmological
model and all its parameters.  \cite{1937ApJ....86..217Z} drew attention to the
former, and \cite{1964MNRAS.128..307R,1966MNRAS.132..101R} pointed out the
latter, all long before lenses were discovered.  The difficulty with actually
doing this, however, became apparent soon after the discovery of the first lens
by \cite{1979Natur.279..381W}.  In the first ever paper on lens modelling,
\cite{1981ApJ...244..736Y} found that many plausible mass distributions could
reproduce the data.

@@

  Being under-constrained, it is then {\it necessary} to explore model
  degeneracies rather than finding a single `best-fit'
  solution. Free-form models are more commonly used with cluster
  lenses
  \citep{2006ApJ...652L...5S,2009ApJ...690..154S,2009A&A...500..681M,2013arXiv1304.2393S},
  but can be used with galaxy lenses as well, where their less
  restrictive assumptions can be important.  For example, in
  time-delay galaxy lenses, parametric model measures of the Hubble parameter $H_0$ have historically been at 
  tension with independent measures 
  \citep[e.g.][]{2002astro.ph..4043K,2002ApJ...578...25K}; these are
  resolved once the less restrictive assumptions of free-form models
  are permitted \citep{2007ApJ...667..645R}.  Hybrid methods, using a
  mass grid on top a parametric model, have also been explored
  \citep[e.g.,][]{2010MNRAS.408.1969V}.

\item {\bf Model ensembles:} Model ensembles, exploring a diverse
  range of possible mass distributions that nonetheless all fit the data,
  are a way of combating the non-uniqueness of models.  Such ensembles are
  possible in parametric models \citep{1999AJ....118...14B} but are more
  common in free-form models, where -- since such models are deliberately under-constrained -- they become vital 
  \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.

\item {\bf Stellar kinematic constraints:} This was first suggested by
  \citet{2002MNRAS.337L...6T} as a means to break lensing
  degeneracies. The idea is that stellar kinematics can provide an
  independent estimate of the Einstein radius, via the virial theorem:
%
\begin{equation}
  \frac{\langle v^2_\mathrm{los}\rangle}{c^2} \approx
  \frac{\theta_E}{6\pi} \frac{D_S}{D_{LS}}
\label{eqn:virial}
\end{equation}
%
where $\langle v^2_\mathrm{los}\rangle$ is the projected stellar
velocity dispersion, and the above relation becomes exact for
isothermal lenses. This can then be used to probe cosmological parameters if lenses are known to be isothermal \citep[e.g.][]{2012MNRAS.424.2864C}; or to break the steepness degeneracy in the more general situation (see \S\ref{sec:kinematics}). The technique has since been applied to many lenses \citep[e.g.][]{2006ApJ...649..599K,2008ApJ...682..964B}.  Going further, the
use of two-dimensional kinematics \citep{2011MNRAS.415.2215B} is
especially interesting.

\item {\bf Stellar mass constraints:} The stellar mass in a lens can be
    inferred from photometry and compared with the total mass
    \citep[e.g.][]{1998ApJ...509..561K,2000ApJ...543..131K,2003ApJ...587..143R,2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.  Since
    the inferred stellar mass depends on the assumed IMF, lenses in which
    stellar mass dominates can be used to derive upper bounds on the stellar
    $M/L$ \citep{2010MNRAS.409L..30F}. Lower bounds on stellar $M/L$ have also
    recently been claimed by fitting $\Lambda$CDM semi-analytic models to the tilt of the fundamental plane \citep{2013MNRAS.428.3183D}.

@@

There are three further key modelling ideas in the literature that we will not
touch upon in this present work: to use X-ray intensity and temperature
profiles as a mass constraint \citep[e.g.][]{2013ApJ...765...25N}; and to model
multiple lenses simultaneously, with one or more cosmological parameters
variable but shared between the lenses. This latter strategy has been used to
constrain $H_0$ from time delay lenses
\citep{2006ApJ...652L...5S,2008ApJ...679...17C,2010ApJ...712.1378P} and
recently the cosmological parameters $\Omega$ as well
\citep{2014MNRAS.437..600S}.  Third, it is in principle possible to estimate
the $\Omega$ parameters even from a single lens, if there are lensed sources at
multiple redshifts \citep{2014MNRAS.437.2461L} or by using additional priors 
\citep{2010Sci...329..924J,2013arXiv1306.4732S}.

@@

\subsection{A post-processing module for stellar kinematics}\label{sec:glasskinematics} 
Similarly to the null-space constraint (\secref{sec:glassextraimages}), stellar
kinematic constraints constitute a non-linear prior on the mass map and must be
applied in post-processing. We sweep through the model ensemble performing an
Abel deprojection to determine $\Mddd(r)$ from the projected surface density
$\Sigma(R)$ assuming spherical symmetry
\citep[e.g.][]{2008gady.book.....B,2008MNRAS.390.1647B}: 
%
\begin{eqnarray} 
    \Mddd(r) & = & 2\pi \int_0^r R \Sigma(R) dR - 4r^2 \int_0^{\pi/2} \Sigma\left(x\right) \left(\frac{1}{\cth[2]} \right. \nonumber \\ 
    & & \left. - \frac{\sth}{\cth[3]} \arctan\left(\frac{\cth}{\sth}\right) \right) \dth
\end{eqnarray}
%
where $M(<r)$ is the projected enclosed mass evaluated at 3D radius $r$; and $x = r/\cth$.

@@

\begin{enumerate}
\item one double and one extended double;
\item one quad and one extended quad;
\item two 2-source quads with varying redshift contrast.
\end{enumerate}
The `extended' configurations use multiple point sources at the same redshift
to simulate an extended source that will produces an arc-like image.
\figref{arrival surfaces} shows the lens configurations for the \mockBC\
galaxy.  The configurations for the other galaxies are similar. Within the
names, the labels R1, R2, R3, refer to the redshift of the sources. We have
chosen R1=1.72, R2=0.72, and R3=0.51 so that the radial distribution of the
images is nearly equal. For all mocks, we do not apply any external shear field.

@@

In all cases -- despite applying no external shear to the mock lenses -- we allow a broad range of external shear in our lens model reconstructions. \Glass\ correctly returns a small or zero shear in all cases. It is possible that more complex shear fields present in real lensing galaxies could introduce further degeneracies beyond those discussed here. However, any such shear field can, at least in principle, be constrained by data (e.g. combining
weak lensing constraints, or assuming that the shear field correlates with
visible galaxies -- e.g. \citealt{2009A&A...500..681M,2011ApJ...726...84W}).

@@

We can also more directly probe the recovery of the shape of the mass
distribution by defining a global measure of lens shape:
%
\begin{equation} 
    s \equiv \lambda_1/\lambda_2
\end{equation} 
%
where $\lambda_1$ and $\lambda_2$ are the eigenvalues of the 2D inertia tensor:
%
% \begin{gather}
%    I_{xx} = \sum_{\vec\theta} M(\vec\theta) \theta^2_y \quad ; \quad
%    I_{yy} = \sum_{\vec\theta} M(\vec\theta) \theta^2_x \\
%    I_{xy} = I_{yx} = - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \nonumber
%    \label{eqn:inertia}
% \end{gather}
%
\begin{equation}
\left(
\begin{matrix}
   \sum_{\vec\theta} M(\vec\theta) \theta^2_y 
    & - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y \\
    - \sum_{\vec\theta} M(\vec\theta) \theta_x \theta_y
    & \sum_{\vec\theta} M(\vec\theta) \theta^2_x
\end{matrix}
\right).
    \label{eqn:inertia}
\end{equation}
%
We always take $\lambda_1$ to be the largest value. As with $f_R$ and
$f_\theta$, we only consider mass up to one radial position passed the
outermost image and compute the fractional error as:
%
\begin{equation} \label{ferror shape}
  f_\mathrm{shape} = \left|s - \tilde s\right|  / \tilde s
\end{equation}
%
where $\tilde s$ is the shape of the mock galaxy. The distribution of
$f_\mathrm{shape}$ for each mock galaxy and each test case is shown in
\figref{shape results}.  Interestingly, for this global shape parameter
recovery it appears more important to have time delay data and/or a central
image (T,M) than to have a quad or multiple sources with wide redshift
separation. In all cases, the stellar mass little-aids the recovery, reflecting
the fact that $s$ is heavily weighted towards the shape at the {\it edge} of
the mass map, rather than at the centre where the stars may dominate the
potential (see \eqnref{eqn:inertia}).

@@

\item Stellar masses -- for lenses
where the stars dominate the central potential -- can also break the steepness
degeneracy, giving a recovery for doubles almost as good as having a quad with time delay data, or
multiple source redshifts;

@@

In this appendix, we explore the effect of the radial symmetry prior.
\figref{fig:no_symm_prior} shows results for a single quad (top two rows) and an
extended double (bottom two rows) without the radial prior; in both cases, we do not use the stellar mass
constraints. The bottom row of each group uses time delay data. Without time delay data or the radial symmetry prior, the results for the quad are poor -- particularly the shape recovery. Including time delays, the results are similar to the case with the radial prior (\figref{reconstruction} and \figref{2d mass reconstruction}). Similarly, for the extended double the results without time delays are poor. Even with time delays, the shape is not well recovered without the radial prior, as expected.

\begin{figure*}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d.pdf}\\
%
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-a-1.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-b-1.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-c-1.pdf}
\includegraphics[width=0.24\textwidth]{BCQuadR1a-nosymm_Tms-appendix-d-1.pdf}\\
%
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-a.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-b.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-c.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_tms-appendix-d.pdf}
%
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-a-1.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-b-1.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-c-1.pdf}
\includegraphics[width=0.24\textwidth]{BCExtendedDoubleR1-nosymm_Tms-appendix-d-1.pdf}
\caption{Results for a single quad (upper two rows) and an extended double (lower two rows)
    without the radial symmetry prior; the bottom row of each group uses time delay data. The stellar
    mass constraint has not been used in any of these examples. Figures and symbols are as in \figref{reconstruction} and
    \figref{2d mass reconstruction}.}
\label{fig:no_symm_prior}
\end{figure*}
